---
title: "STAT545hw01"
author: "Caroline"
date: "September 15, 2018"
output: html_document
---

# Data frame exploration

# Run 'install.packages("gapminder") in the console
# Load the 'gapminder' package using the 'library' function
```{r}
library(gapminder)
```

# Explore what the first few rows of the gapminder dataset looks like by using the 'head' command
```{r}
head(gapminder)
```
# Now let's use 'summary' to get some more information about the gapminder dataset
# Summary shows the median, mean, minimum and maximum values for each column in the dataset
```{r}
summary(gapminder)
```
# We can use the 'ncol' command to determine the number of columns in the dataset
```{r}
ncol(gapminder)
```
# The 'str' function shows the structure of the dataset
```{r}
str(gapminder)
```
# Using the plot function creates graphs of how all of the variables in the dataset relate to each other
```{r}
plot(gapminder)
```
# To get your final output as a PDF or html, click the 'Knit' button at the top of the page
